Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation

### 2022-03-17 Codes/PrepareResults.rmd

# --- MB function to N --- #
vis_MB_curve <- 
  ggplot(res_y_dt[variable=="Yield"]) +
    geom_line(
      aes(x=N, y=value, color=factor(group)), size=1
    ) +
    geom_point(data= sub_dt, aes(x=opt_N, y=value, alpha = "Yield at EONR"), color = "red", size = 2) +
    # geom_segment(data = sub_dt, aes(x = N, xend=N, y = value, yend=-Inf), linetype = "dashed") +
    scale_alpha_manual(
      name = NULL,
      values = 1,
      breaks = "Yield at EONR",
      guide = guide_legend(override.aes = list(linetype = 0,
        shape = 16,
        color = "red")
        ) 
    ) +
    labs(y = "Yield (kg/ha)") +
    labs(x = "N (kg/ha)") +
    theme_dist +
    theme(legend.title = element_blank()) +
    guides(color=guide_legend(nrow=2, byrow=TRUE))
```

@@

# find_examples_main  <- 
#   res_pred %>%
#   .[variable == "BRF" & aa_n==N,] %>%
#   .[, y_diff_brf := abs(yield - value)] %>%
#   .[y_diff_brf < 700, unique_subplot_id]

@@

# low <- 
#   res_true[aa_n == tg_N_rate[1]] %>%
#   get_rows_optN(data=., value = 0.2, range = 0.1) %>%
#   .[unique_subplot_id %in% find_examples_main] %>%
#   # .[unique_subplot_id %in% sample(unique(unique_subplot_id), size = 1),] %>%
#   .[, unique_subplot_id] %>%
#   unique()

# # length(low)

# medium <-
#    res_true[aa_n == tg_N_rate[1]] %>%
#   get_rows_optN(data=., value = 0.5, range = 0.1) %>%
#   .[unique_subplot_id %in% find_examples_main] %>%
#   # .[unique_subplot_id %in% sample(unique(unique_subplot_id), size = 1),] %>%
#   .[, unique_subplot_id] %>%
#   unique()

# high <- 
#   res_true[aa_n == tg_N_rate[3]] %>%
#   get_rows_optN(data=., value = 0.9, range = 0.1) %>%
#   .[unique_subplot_id %in% find_examples_main] %>%
#   .[unique_subplot_id %in% sample(unique(unique_subplot_id), size = 1), unique_subplot_id] %>%
#   unique()

# vis_res_true <- res_true[unique_subplot_id %in% c(low, medium, high)]
# vis_res_pred <- res_pred[unique_subplot_id %in% c(low, medium, high)]

# low: *13_41*, 15_34
# medium: *8_41*, 8_42, 27_10
# high: 4_21

vis_res_true <- 
  res_true[unique_subplot_id %in% c("15_34", "8_41", "4_21")] %>%
  .[,site := case_when(
    unique_subplot_id == "15_34" ~ "site 1",
    unique_subplot_id == "8_41" ~ "site 2",
    unique_subplot_id == "4_21" ~ "site 3",
    )]

vis_res_pred <- 
  res_pred[unique_subplot_id %in% c("15_34", "8_41", "4_21")] %>%
  .[,site := case_when(
    unique_subplot_id == "15_34" ~ "site 1",
    unique_subplot_id == "8_41" ~ "site 2",
    unique_subplot_id == "4_21" ~ "site 3",
    )]

vis_MB_BRF_y <- 
  ggplot() +
    # --- true yield response curve --- #
    geom_line(
      data=vis_res_true, aes(x=N, y=yield, color = site), size=1
    ) +
    # --- Predicted yield points --- #
    geom_point(
      data=vis_res_pred, aes(x=N, y=value, color = site, alpha = "Predicts"), shape=2, size = 2, stroke = 1
    ) +
    # --- Yield at applied N rate --- #
    geom_point(data = vis_res_true[aa_n==N], aes(x=aa_n, y= yield, alpha = "True yield at actual N rate that was applied"), color = 'blue', size = 2) +
    facet_wrap(~variable) +
    scale_alpha_manual(
      name = NULL,
      values = c(1, 1),
      breaks = c("Predicts", "True yield at actual N rate that was applied"),
      guide = guide_legend(override.aes = list(linetype = c(0, 1),
        shape = c(2, 16),
        color = c("black", "blue")) 
        ) 
    ) +
    labs(y = "Yield (kg/ha)") +
    labs(x = "N (kg/ha)") +
    theme_dist +
    theme(legend.title = element_blank()) +
    guides(color=guide_legend(nrow=2, byrow=TRUE))
```

@@

## Figure (RMSE of EONR vs RMSE of yield for RF abd BRF)

```{r}
fig_y_optN <-
  res_y_test %>%
  .[Method %in% c("RF", "BRF", "CNN")] %>%
  ggplot(aes(x = rmse_y, y = rmse_optN)) +
  geom_point(size = 0.5) +
  facet_grid(Model ~ Method) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  stat_regline_equation(
    label.x = 2050, label.y = 90,
    aes(label = ..rr.label..),
    size = 3
  ) +
  guides(
    fill = guide_legend(keywidth = 1, keyheight = 1),
    linetype = guide_legend(keywidth = 3, keyheight = 1),
    colour = guide_legend(keywidth = 3, keyheight = 1)
  ) +
  ylim(NA, 95) +
  labs(y = " RMSE of EONR Estimation (kg/ha)") +
  labs(x = " RMSE of Yield Prediction (kg/ha)") +
  theme_dist
```

>>>>

# --- MB function to N --- #
vis_MB_curve <- 
  ggplot(res_y_dt[variable=="Yield"]) +
    geom_line(
      aes(x=N, y=value, group=factor(group))
    ) +
    geom_point(data= sub_dt, aes(x=opt_N, y=value, alpha = "Yield at EONR"), color = "red", size = 1.5) +
    # geom_segment(data = sub_dt, aes(x = N, xend=N, y = value, yend=-Inf), linetype = "dashed") +
    scale_alpha_manual(
      name = NULL,
      values = 1,
      breaks = "Yield at EONR",
      guide = guide_legend(override.aes = list(linetype = 0,
        shape = 16,
        color = "red")
        ) 
    ) +
    labs(y = "Yield (kg/ha)") +
    labs(x = "N (kg/ha)") +
    theme_dist +
    theme(legend.title = element_blank()) +
    guides(color=guide_legend(nrow=2, byrow=TRUE))
```

@@

find_examples_main  <- 
  res_pred %>%
  .[variable == "BRF" & aa_n==N,] %>%
  .[, y_diff_brf := abs(yield - value)] %>%
  .[y_diff_brf < 500, unique_subplot_id]
  # .[y_diff_brf < 500 & y_diff_brf < 1000, unique_subplot_id]

@@

# low <- 
#   res_true[aa_n == tg_N_rate[3]] %>%
#   get_rows_optN(data=., value = 0.9, range = 0.1) %>%
#   .[unique_subplot_id %in% find_examples_main] %>%
#   # .[unique_subplot_id %in% sample(unique(unique_subplot_id), size = 1),] %>%
#   .[, unique_subplot_id] %>%
#   unique()

# length(low)
# x <- 16
# i= x:(x+1)
# vis_res_true <- res_true[unique_subplot_id %in% low[i]]
# vis_res_pred <- res_pred[unique_subplot_id %in% low[i]]
# ggplot() +
#     geom_line(
#       data=vis_res_true, aes(x=N, y=yield, color = unique_subplot_id)
#     ) +
#     geom_point(
#       data=vis_res_pred, aes(x=N, y=value, color = unique_subplot_id, alpha = "Predicts"), shape=2, size = 1.5
#     ) +
#     geom_point(data = vis_res_true[aa_n==N], aes(x=aa_n, y= yield, alpha = "True yield at actual N rate that was applied"), color = 'blue', size = 1.5) +
#     facet_wrap(~variable) +
#     scale_alpha_manual(
#       name = NULL,
#       values = c(1, 1),
#       breaks = c("Predicts", "True yield at actual N rate that was applied"),
#       guide = guide_legend(override.aes = list(linetype = c(0, 1),
#         shape = c(2, 16),
#         color = c("black", "blue")) 
#         ) 
#     ) +
#     labs(y = "Yield (kg/ha)") +
#     labs(x = "N (kg/ha)") +
#     theme_dist +
#     theme(legend.title = element_blank()) +
#     guides(color=guide_legend(nrow=2, byrow=TRUE))

# tg_N_rate <- N_rate[2]
# low: 13_41, 15_34, 15_35, 11_40
# medium: 8_41, *8_42*, *8_43*, 27_10
# high: 4_21

# tg_N_rate <- N_rate[3]
# **2_18**, 10_42 ***6_47***

# tg_N_rate <- N_rate[4]
# 10_49

# final
# + *2_18* (more than 14500)
# + *8_42* (11500) 
# + *8_43* (11300)
# + **6_47** (11100)

# c("2_18", "8_42")
# c("2_18", "6_47") **

# vis_res_true <- res_true[unique_subplot_id %in% c("2_18", "6_47")]
# vis_res_pred <- res_pred[unique_subplot_id %in% c("2_18", "6_47")]
# ggplot() +
#     geom_line(
#       data=vis_res_true, aes(x=N, y=yield, color = unique_subplot_id)
#     ) +
#     geom_point(
#       data=vis_res_pred, aes(x=N, y=value, color = unique_subplot_id, alpha = "Predicts"), shape=2, size = 1.5
#     ) +
#     geom_point(data = vis_res_true[aa_n==N], aes(x=aa_n, y= yield, alpha = "True yield at actual N rate that was applied"), color = 'blue', size = 1.5) +
#     facet_wrap(~variable) +
#     scale_alpha_manual(
#       name = NULL,
#       values = c(1, 1),
#       breaks = c("Predicts", "True yield at actual N rate that was applied"),
#       guide = guide_legend(override.aes = list(linetype = c(0, 1),
#         shape = c(2, 16),
#         color = c("black", "blue")) 
#         ) 
#     ) +
#     labs(y = "Yield (kg/ha)") +
#     labs(x = "N (kg/ha)") +
#     theme_dist +
#     theme(legend.title = element_blank()) +
#     guides(color=guide_legend(nrow=2, byrow=TRUE))

vis_res_true <- 
  res_true[unique_subplot_id %in% c("2_18", "6_47")] %>%
  .[,site := case_when(
    unique_subplot_id == "2_18" ~ "site 1",
    unique_subplot_id == "6_47" ~ "site 2"
    )]

vis_res_pred <- 
  res_pred[unique_subplot_id %in% c("2_18", "6_47")] %>%
  .[,site := case_when(
    unique_subplot_id == "2_18" ~ "site 1",
    unique_subplot_id == "6_47" ~ "site 2"
    )]

vis_MB_BRF_y <- 
  ggplot() +
    # --- true yield response curve --- #
    geom_line(
      data=vis_res_true, aes(x=N, y=yield, group = site)
    ) +
    # --- Predicted yield points --- #
    geom_point(
      data=vis_res_pred, aes(x=N, y=value, group = site, alpha = "Predicts"), shape=2, size = 1.5
    ) +
    # --- Yield at applied N rate --- #
    geom_point(data = vis_res_true[aa_n==N], aes(x=aa_n, y= yield, alpha = "True yield at actual N rate that was applied"), color = 'blue', size = 1.5) +
    facet_wrap(~variable) +
    scale_alpha_manual(
      name = NULL,
      values = c(1, 1),
      breaks = c("Predicts", "True yield at actual N rate that was applied"),
      guide = guide_legend(override.aes = list(linetype = c(0, 1),
        shape = c(2, 16),
        color = c("black", "blue")) 
        ) 
    ) +
    labs(y = "Yield (kg/ha)") +
    labs(x = "N (kg/ha)") +
    theme_dist +
    theme(legend.title = element_blank()) +
    guides(color=guide_legend(nrow=2, byrow=TRUE))
```

@@

## Figure (RMSE of EONR vs RMSE of yield for RF and BRF)

```{r}
# fig_y_optN <-
  # res_y_test %>%
  # .[Method %in% c("RF", "BRF", "CNN")] %>%
  # ggplot(aes(x = rmse_y, y = rmse_optN)) +
  # geom_point(size = 0.5) +
  # facet_grid(Model ~ Method) +
  # geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  # stat_regline_equation(
  #   label.x = 2050, label.y = 90,
  #   aes(label = ..rr.label..),
  #   size = 3
  # ) +
  # guides(
  #   fill = guide_legend(keywidth = 1, keyheight = 1),
  #   linetype = guide_legend(keywidth = 3, keyheight = 1),
  #   colour = guide_legend(keywidth = 3, keyheight = 1)
  # ) +
  # ylim(NA, 95) +
  # labs(y = " RMSE of EONR Estimation (kg/ha)") +
  # labs(x = " RMSE of Yield Prediction (kg/ha)") +
  # theme_dist
```

```{r}
vis_RMSE_y_eonr <- 
  res_y_test %>%
  .[sim %in% c(10, 20, 30) & Method %in% c("RF", "BRF", "CNN") & Model == "aabbyytt"] %>%
  ggplot() +
  geom_point(aes(x = rmse_y, y = rmse_optN, shape = Method, fill = factor(sim)), size = 2) +
  scale_shape_manual(values = c(21, 23, 25)) +
  guides(
    fill = guide_legend(override.aes=list(shape=21))
  ) +
  labs(fill="Simulation Round", shape="Method") +
  # guides(fill = "none") +
  # facet_wrap( ~ Model, ncol = 2) +
  ylim(NA, 95) +
  labs(y = " RMSE of EONR Estimation (kg/ha)") +
  labs(x = " RMSE of Yield Prediction (kg/ha)") +
  theme_dist 
```

### 2022-03-17 Writing/appendix.rmd

```{r, vis-MB-BRF-y, fig.cap = "Figure G.1: Predicted (scenario: aby)"}
vis_MB_BRF_y
```

@@

>>>>

```{r, vis-MB-BRF-y, fig.width=7, fig.height=5, fig.cap = "Figure G.1: Predicted (scenario: aabbyytt)"}
vis_MB_BRF_y
```

@@

## Appendix I: The Relationship between Yield and EONR Prediction Performances (scenario: aabbyytt)

```{r, vis-RMSE-y-eonr, fig.width=5, fig.height=5, fig.cap = "Figure I.1: The Relationship between Yield and EONR Prediction Performances"}
vis_RMSE_y_eonr
```
